% https://tabs.ultimate-guitar.com/user/tab/view?h=jpUXg-25SxAiXLR_6T1sLVwF

\beginsong{Greensleeves}[by={Traditionell}, index={Alas, my love, you do me wrong}]
\beginverse
A\[Dm]las, my \[F]love, you \[C]do me \[Am]wrong,
to \[Dm]cast me off disc\[A]ourteously.
For \[Dm]I have \[F]loved you \[C]well and \[Am]long,
de\[Dm]lighting \[A7]in your \[Dm]company.
\endverse

\beginchorus
\[F]Greensleeves was \[C]all my \[Am]joy,
\[Dm]Greensleeves was \[A]my delight
\[F]Greensleeves was my \[C]heart of \[Am]gold,
and \[Dm]who but my \[A7]lady \[Dm]greensleeves.
\endchorus

\beginverse
Your \[Dm]vows you've \[F]broken, \[C]like my \[Am]heart,
Oh, \[Dm]why did you so en\[A]rapture me?
Now \[Dm]I re\[F]main in a \[C]world a\[Am]part
But \[Dm]my heart re\[A7]mains in cap\[Dm]tivity.
\endverse

\beginchorus \textnote{Refrain} \endchorus

\beginverse
\[F]I have been ready \[C]at your \[Am]hand,
To \[Dm]grant whatever \[A]you would crave,
\[F]I have both wagered \[C]life and \[Am]land,
Your \[Dm]love and good-\[A7]will \[Dm]for to have.
\endverse

\beginchorus \textnote{Refrain} \endchorus

\beginverse
If \[Dm]you in\[F]tend thus \[C]to dis\[Am]dain,
It \[Dm]does the more en\[A]rapture me,
And \[Dm]even \[F]so, I \[C]still re\[Am]main
A \[Dm]lover \[A7]in cap\[Dm]tivity.
\endverse

\beginchorus \textnote{Refrain} \endchorus

\beginverse
My\[F] men were clothed \[C]all in \[Am]green,
And \[Dm]they did ever \[A]wait on thee;
\[F]All this was gallant \[C]to be \[Am]seen,
And \[Dm]yet thou \[A7]wouldst not \[Dm]love me.
\endverse

\beginchorus \textnote{Refrain} \endchorus

\beginverse
Thou \[Dm]couldst de\[F]sire no \[C]earthly \[Am]thing,
But \[Dm]still thou hadst it \[A]readily.
Thy \[Dm]music \[F]still to \[C]play and \[Am]sing;
And \[Dm]yet thou \[A7]wouldst not \[Dm]love me.
\endverse

\beginchorus \textnote{Refrain} \endchorus

\beginverse
Well, \[Dm]I will \[F]pray to \[C]God on \[Am]high,
That \[Dm]thou my constancy \[A]mayst see,
And that \[Dm]yet \[F]once be\[C]fore I \[Am]die,
Thou \[Dm]wilt vouch\[A7]safe to \[Dm]love me.
\endverse

\beginchorus \textnote{Refrain} \endchorus

\beginverse
Ah,\[F] Greensleeves, now \[C]farewell, a\[Am]dieu,
To \[Dm]God I pray to \[A]prosper thee,
For \[F]I am still thy \[C]lover \[Am]true,
Come \[Dm]once a\[A7]gain and \[Dm]love me.
\endverse
\endsong
